Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 \MakeLowercase{b}

### 2018-10-04 ms.tex
some proofreading of the red text.

We posit that the initial analysis of the 2013 Subaru spectrum \citep{kawahara2013starspots} that found a temperature and log(g) of 4950 K and 3.9 log(cm/s$^{-2}$) was affected by insufficient signal to noise in the spectrum.
The 2013 data has a 30\% smaller count rate (in e$^-$/s) than the 2015 data likely because the 2013 weather and guiding were sub-optimal.
On top of that, the total exposure time for the 2013 observations was only 1.5 hours.
The consequence of the increased noise in the 2013 spectra affected the interpretation of this high resolution spectrum.
For example, the SNR of the Na D lines was $\sim$ 30, which is near the threshold needed for the \citet{takeda2005specFGKdwarfs} equivalent width method employed in the initial analysis.
We therefore conclude that the noise in the spectrum affected the stellar parameters rather than gas absorption from sublimating dust grains.
\added{
\section{Spectral Energy Distribution and Parallax}\label{sec:SED}

We also confirm our finding that the star is a main sequence using the Gaia DR2 parallax of 1.617 $\pm$ 0.030 mas \citep{gaia2016mission,gaia2018dr2,luri2018parallaxes}.
We follow the methodology from \citet{stassun2017gaiaRadiiMasses}, which is to estimate the bolometric flux from the spectral energy distribution and invert the Stefan-Boltman law to solve for the radius.
For the measured spectral energy distribution, we use the VizieR photometry service and fit this with a representative 4600 K \citet{castelli2004models} model and a (E-B)=0.05 diffuse Milky Way extinction model \citep{cardelli1989}.
We use the \texttt{pysynphot} tool \citep{lim2015pysynphot} to calculate the model and extinction.
We note that the exact stellar model used is less important than finding a function to fit the Spectral Energy Distribution.
When inverting the Stefan-Boltzman law, we assume an effective temperature of 4400 $\pm$ 70 K from our spectral fitting and a photometric error of 5\%, assumed to be dominated by photometric systematics.
Using this method we find a radius of 0.72 $\pm$ 0.03 R$_\odot$, which is consistent with a main sequence star.

While examining the bolometric flux from all available data, we notice that the WISE band 3 and 4 fluxes at 12 $\mu$m and 22 $\mu$m \citep{wright2010wise} are significantly in excess of a \citet{castelli2004models} stellar model, as shown in Figure \ref{fig:SED}.
This is also true of the disintegrating system K2-22 b.
These infrared fluxes may arise from dust created by the disintegrating planet and radiatively pushed out to a larger radius to form a disk or ring.
Further investigation of the infrared excesses should be explored observationally and theoretically.

@@

High values of $f_S$ are possible for longitudinally symmetric distributions of active regions, such as a latitudinal band or polar spot.
Polar spots are indeed observed on rapidly rotating stars via Doppler imaging \citep{strassmeier2009starspots}; however, one would be unlikely on \sha, given its relatively long rotation period.
Additionally, the large physical size of \sha, as indicated by a transit duration longer than the time to cross the star, means that spots are likely to be crossed and thus this diminish the transit source effect further.
In this light, \sha's 30\% observed transit depth variation would require a pathological distribution of stellar activity to be explained by un-occulted spots.
If the spot distribution is polar or distributed in a latitudinal band, this would produce a bias at all epochs, unlike the time-dependent transit depth variations observed in \sha.
Therefore, the conclusion from \citet{croll2015starspots} that unocculted spots are unlikely to cause the correlation between transit depth and stellar flux is likely correct even when considering a more realistic scaling relation between spot covering fraction and rotational modulation amplitude.
}

>>>>

We posit that the initial analysis of the 2013 Subaru spectrum \citep{kawahara2013starspots} that found a temperature and log(g) of 4950 K and 3.9 log(cm/s$^{-2}$) was affected by insufficient signal to noise in the spectrum.
The 2013 data has a 30\% smaller count rate (in e$^-$/s) than the 2015 data likely because the 2013 weather and guiding were sub-optimal.
On top of that, the total exposure time for the 2013 observations was only 1.5 hours.
The consequence of the increased noise in the 2013 spectra affected the interpretation of this high resolution spectrum.
For example, the SNR of the Na D lines was $\sim$ 30, which is near the threshold needed for the \citet{takeda2005specFGKdwarfs} equivalent width method employed in the initial analysis.
We therefore conclude that the noise in the spectrum affected the stellar parameters rather than gas absorption from sublimating dust grains.
\added{
\subsection{Spectral Energy Distribution and Parallax}\label{sec:SED}

We also confirm our finding that the star is a main sequence using the Gaia DR2 parallax of 1.617 $\pm$ 0.030 mas \citep{gaia2016mission,gaia2018dr2,luri2018parallaxes}.
We follow the methodology from \citet{stassun2017gaiaRadiiMasses}, which is to estimate the bolometric flux from the spectral energy distribution and invert the Stefan-Boltman law to solve for the radius.
For the measured spectral energy distribution, we use the VizieR photometry service and fit this with a representative 4600 K \citet{castelli2004models} model and a (E-B)=0.05 diffuse Milky Way extinction model \citep{cardelli1989}.
We use the \texttt{pysynphot} tool \citep{lim2015pysynphot} to calculate the model and extinction.
We note that the exact stellar model used is less important than finding a function to fit the Spectral Energy Distribution.
When inverting the Stefan-Boltzman law, we assume an effective temperature of 4400 $\pm$ 70 K from our spectral fitting in Section \ref{sec:SpecMatch-Emp} and a photometric error of 5\%, assumed to be dominated by photometric systematics.
Using this method we find a radius of 0.72 $\pm$ 0.03 R$_\odot$, which is consistent with a main sequence star.

While examining the bolometric flux from all available data, we notice that the WISE band 3 and 4 fluxes at 12 $\mu$m and 22 $\mu$m \citep{wright2010wise} are significantly in excess of the \citet{castelli2004models} stellar model, as shown in Figure \ref{fig:SED}.
This is also true of the disintegrating system K2-22 b.
These infrared fluxes may arise from dust created by the disintegrating planet and radiatively pushed out to a larger radius to form a disk or ring.
Further investigation of the infrared excesses should be explored observationally and theoretically.

@@

High values of $f_S$ are possible for longitudinally symmetric distributions of active regions, such as a latitudinal band or polar spot.
Polar spots are indeed observed on rapidly rotating stars via Doppler imaging \citep{strassmeier2009starspots}; however, one would be unlikely on \sha, given its relatively long rotation period.
Additionally, the large physical size of \sha, as indicated by a transit duration longer than the time to cross the star, meaning that spots are likely to be crossed and thus diminish the transit source effect further.
In this light, \sha's $\sim$30\% observed transit depth variation at a $\sim$ 22 day period would require a pathological distribution of stellar activity to be explained by un-occulted spots.
If the spot distribution is polar or distributed in a latitudinal band, this would produce a bias at all epochs, unlike the time-dependent transit depth variations observed in \sha.
Therefore, the conclusion from \citet{croll2015starspots} that unocculted spots are unlikely to cause the correlation between transit depth and stellar flux is likely correct even when considering a more realistic scaling relation between spot covering fraction and rotational modulation amplitude.
}
